Computing volume via non-uniform rectangular infinitesimals

### 2019-08-16 Cav2D/article-template.tex
fixed the figures

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{cav_principle.pdf}
\caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right non-uniform reectangular prism 
due to Cavalieri's principle in $\mathbb{R}^3$.}
\label{fig:cav_principle}
\end{figure}

\noindent
Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column (left solid) as well as a \emph{non-uniform rectangular prism or column} (right solid). The volumes of the two solids in Figure~\ref{fig:cav_principle} are equal due 
to Cavalieri's principle. Note that in this article we use the non-standardized phrase non-unifor rectangular prism or column to refer to a solid that has rectangular 
basis and lateral edges that are either oblique lines or non-linear curves. Moreover, the four lateral edges of the aformentioned solid also need to be translations of one another. In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
lenght and widht both tend to zero as a non-uniform rectangular infinitesimal. \\

>>>>

\begin{figure}[htb]
\centering
\includegraphics[width=0.5\textwidth]{cav_principle.pdf}
\caption{Illustration of Cavalier's principle in $\mathbb{R}^3$. The volume of the left rectangular prism is equal to the volume of the right non-uniform reectangular prism 
due to Cavalieri's principle in $\mathbb{R}^3$. The infinitesimals associated with the two solids are also depicted.}
\label{fig:cav_principle}
\end{figure}

\noindent
Figure~\ref{fig:cav_principle} depicts a classic rectangular prism or column (left solid) as well as a \emph{non-uniform rectangular prism or column} (right solid). The volumes of the two solids in Figure~\ref{fig:cav_principle} are equal due 
to Cavalieri's principle. Note that in this article we use the non-standardized phrase non-unifor rectangular prism or column to refer to a solid that has rectangular 
basis and lateral edges that are either oblique lines or non-linear curves. Moreover, the four lateral edges of the aformentioned solid also need to be translations of one another. In this paper, we will also take the liberty to refer to a non-linear rectangular prism whose base's
lenght and widht both tend to zero as a \emph{non-uniform rectangular infinitesimal}. \\
